07-logistic_regression

### 2019-03-11 journals/07-logistic_regression/07-logistic_regression.Rmd
work during meeting and presentation moved
quick fixes and prepared lime for logisitic regression

```{r}
# Load libraries
library(lime)
library(tidyverse)
```

@@

}

summary(logistic_mains)
```

@@

>>>>

```{r}
# Load libraries
library(furrr)
library(future)
library(lime)
library(tidyverse)

# Source functions
source("../../code/helper_functions.R")
```

@@

@@

```{r}
pca_results <- princomp(hamby224_test %>% select(rf_features) %>% na.omit())
pca_results$loadings
z1 <- pca_results$scores[,1]
z2 <- pca_results$scores[,2]
ggplot(data.frame(z1, z2), aes(x = z1, y = z2)) + 
  geom_point()
biplot(pca_results)
```

### All Input Options of LIME Applied to Main Effects Model

The code below applies the LIME algorithm to the main effects logisitic regression model one time for the following different input cases:

- 2 to 6 quantile bins
- 2 to 6 equally spaced bins
- 2 to 6 tree based bins with `samesource` as the response variable
- 2 to 6 tree based bins with `rfscore` as the response variable
- kernel density estimation
- normal density approximation

It applies LIME using my function `run_lime` to specify the different input values. The outputs from the `lime` function are combined into a list, and the outputs from the `explain` function are combined into dataframe. Both are saved as .rds files.

```{r}
# Apply the run_lime function if the lime results file does not already exist
if(!file.exists("./data/logistic_lime_inputs.rds")) {

  # Specify the input options to use with lime
  logistic_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
                                                  rep(FALSE, 2)),
                               quantile_bins = c(rep(TRUE, 5), 
                                                 rep(FALSE, 5), 
                                                 rep(TRUE, 12)),
                               nbins = c(rep(2:6, 4), 
                                         rep(4, 2)),
                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
                               bin_method = c(rep("quantile_bins", 5),
                                              rep("equally_spaced", 5),
                                              rep("tree", 10),
                                              rep("quantile_bins", 2)),
                               response = c(rep(NA, 10), 
                                            rep("samesource", 5), 
                                            rep("rfscore", 5), 
                                            rep(NA, 2)))

  # Tell R to run the upcoming code in parallel
  plan(multiprocess)

  # Apply lime to the full training data with the specified input options
  logistic_lime_explain <- future_pmap(.l = logistic_lime_inputs,
             .f = run_lime, # run_lime is one of my helper functions
             features = rf_features,
             train = hamby173and252_train,
             test = hamby224_test %>% 
               arrange(case) %>% 
               select(rf_features) %>% 
               na.omit(),
             rfmodel = logistic_mains,
             label = "TRUE",
             nfeatures = 3,
             seed = TRUE)

  # Separate the lime and explain function results from the full data
  logistic_lime <- map(logistic_lime_explain, function(list) list$lime)
  logistic_explain <- map_df(logistic_lime_explain, function(list) list$explain)

  # Name the items in the lime list
  names(logistic_lime) <- map_chr(1:22, function(case) 
      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
              logistic_lime_inputs$bin_continuous[case],
              logistic_lime_inputs$quantile_bins[case],
              logistic_lime_inputs$nbins[case],
              logistic_lime_inputs$use_density[case],
              logistic_lime_inputs$bin_method[case],
              logistic_lime_inputs$response[case]))

  # Turn the lime input options into a dataframe before saving it
  logistic_lime_inputs <- logistic_lime_inputs %>%
    unlist() %>%
    matrix(ncol = length(logistic_lime_inputs), 
           dimnames = list(NULL, names(logistic_lime_inputs))) %>%
    as.data.frame() %>%
    mutate(case = 1:length(logistic_lime_inputs$quantile_bins)) %>%
    select(case, bin_continuous:response)

  # Save the lime objects
  saveRDS(logistic_lime_inputs, "./data/logistic_lime_inputs.rds")
  saveRDS(logistic_lime, "./data/logistic_lime.rds")
  saveRDS(logistic_explain, "./data/logistic_explain.rds")

  # Load in the lime objects
  logistic_lime_inputs <- readRDS("./data/logistic_lime_inputs.rds")
  logistic_lime <- readRDS("./data/logistic_lime.rds")
  logistic_explain <- readRDS("./data/logistic_explain.rds")
